Running `Earth_obs_cleaning` on MCD19A2: Results from CONUS

### 2022-12-20 writing/CONUS_AOD.Rmd
Removed the absolute-error CV.

```{r stratified, echo=FALSE}
dt <- copy(tar_read(initial_cv_l2)$mDT_wPred)
```

@@

```{r shap_rank, echo=FALSE}
# what do the SHAPs tell us?
tar_load(initial_cv_l2)
shaps <- initial_cv_l2$"shap_score"
# sort by importance
df_shap <- data.frame(meanabsshap = round(sort(sapply(abs(shaps), mean), decreasing = TRUE), 4))
kbl(df_shap, col.names = "Mean |SHAP|") %>% row_spec(0, bold=TRUE)
# df_shap$variable <- row.names(df_shap)
# ft_shap <- flextable(df_shap[, c(2, 1)])
# ft_shap <- set_header_labels(ft_shap, list(variable = "Variable", meanabsshap = "Mean Absolute SHAP"))
# ft_shap
```
Summary visualization of SHAP contributions

```{r shap_summary, echo=FALSE, dev='png', dpi=300, eval=FALSE}
shap_long <- shap.prep(shap_contrib = initial_cv_l2$shap_score,
                       X_train = initial_cv_l2$mDT_wPred[, names(initial_cv_l2$shap_score), with = F])
# **SHAP summary plot**
shap.plot.summary(shap_long)
```

>>>>

```{r stratified, echo=FALSE}
dt <- copy(tar_read(initial_cv)$mDT_wPred)
```

@@

```{r shap_rank, echo=FALSE}
# what do the SHAPs tell us?
tar_load(initial_cv)
shaps <- initial_cv$"shap_score"
# sort by importance
df_shap <- data.frame(meanabsshap = round(sort(sapply(abs(shaps), mean), decreasing = TRUE), 4))
kbl(df_shap, col.names = "Mean |SHAP|") %>% row_spec(0, bold=TRUE)
# df_shap$variable <- row.names(df_shap)
# ft_shap <- flextable(df_shap[, c(2, 1)])
# ft_shap <- set_header_labels(ft_shap, list(variable = "Variable", meanabsshap = "Mean Absolute SHAP"))
# ft_shap
```
Summary visualization of SHAP contributions

```{r shap_summary, echo=FALSE, dev='png', dpi=300, eval=FALSE}
shap_long <- shap.prep(shap_contrib = initial_cv$shap_score,
                       X_train = initial_cv$mDT_wPred[, names(initial_cv_l2$shap_score), with = F])
# **SHAP summary plot**
shap.plot.summary(shap_long)
```
